---
title: "CV"
author: "Anders Gonçalves da Silva, PhD"
editor_options:
  chunk_output_type: console
output:
  pdf_document:
    latex_engine: pdflatex
    template: /Users/andersgoncalves/Dropbox/projects/cv/templates/svm-latex-cv.tex
  html_document:
    df_print: paged
fontawesome: yes
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
geometry: margin=1in
github: andersgs
jobtitle: Bioinformatician | Microbiological Diagnostic Lab Public Health Laboratory
keywords: R Markdown, academic CV, template
linkcolor: blue
email: anders.goncalves@unimelb.edu.au
address: Peter Doherty Institute for Immunity and Infection, The University of Melbourne
twitter: '@drandersgs'
updated: no
urlcolor: blue
---

# Employment

*Microbiological Diagnostic Unit Public Health Laboratory, The Univesity of Melbourne*

Bioinformatician \hfill 2015-

*Ornithology Lab, Monash University*

Postdoctoral Researcher \hfill 2012-2015

*CSIRO Marine and Atmospheric Research*

Postdoctoral Fellow \hfill 2009-2012

*Ecological and Conservation Genomics Lab, University of British Columbia*

Postdoctoral Teaching and Research Fellow \hfill 2007-2009


# Education

*Columbia University*, PhD Ecology and Evolutionary Biology \hfill 2007

*Columbia University*, MSc Ecology and Evolutionary Biology \hfill 2004

*Columbia University*, MA Conservation Biology \hfill 2003

*Universidade Estadual de Campinas*, BSc Biology \hfill 2000


# Service and Leadership

*Leadership* of the MDU PHL Bioinformatics Team.

*Leadership* of the national CDGN Bioinformatics Working Group.

*Leadership* of the MDU/DHHS Partnership Grant.

*Leadership* in AusTrakka (data sharing for public health).

*Leadership* in development of best practices for accreditation of Bioinformatics software for use in public health.

*Leadership* in development of national proficiency testing programs for Next Generation Sequencing and Bioinformatics software.

*Leadership* in development of a national pathogen surveillance platform based on genomic data.


# Publications

## Journal Articles

```{r, echo=FALSE, results='asis'}
library(RefManageR)
library(glue)
bib <- ReadBib("bibfiles/publications.bib")
for(year in 2018:2008) {
  print(glue("### {year}"))
  print(bib[year = glue("{year}")],  .opts = list(bib.style = "authoryear"))
  print(glue(" "))
}
```

## Reports

```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/reports.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

## Book Chapters

```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/book-chapter.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

## Recent Conference Presentations
```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/conferences.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

# Students

## PhD

*Courtney Lane* --- Department of Microbiology and Immunology, The University of Melbourne

*Andrew Buultjens* --- Department of Microbiology and Immunology, The University of Melbourne

*Lee Peacock* --- School of Biological Sciences, Monash University

## MSc

*Alistair Edwards* --- Faculty of Science, The University of Melbourne *[Deferred]*

*Andre Tan* --- Faculty of Science, The University of Melbourne [Completed]

*Gabriela Pinho* --- Instituto Nacional de Pesquisas da Amazônia [Completed]

## Honours

*Tiffany Miller-Scott* --- School of Biological Sciences, Monash University [Completed]

# Teaching

## Workshops

Genomic Epidemiology of Infectious Diseases. McGill Summer Institute in Infectious Diseases & Global Health \hfill 2018

Genomic Epidemiology of Infectious Diseases. McGill Summer Institute in Infectious Diseases & Global Health \hfill 2017 

Introductory Course in Public Health Microbial Genomics \hfill 2017

Introductory Course in Public Health Microbial Genomics \hfill 2016

Australian Pathogen Bioinformatics Symposium (ANU) \hfill 2014

Population and landscape genomics workshop (ANU) \hfill 2014

## Units

BINF90002: Elements of Bioinformatics (Lecturer) - The University of Melbourne \hfill 2017

BIOL 203: Introduction to Ecology (Instructor) – University of British Columbia \hfill 2009

GEOG 213: Introduction to Environmental Issues (Instructor) – University of British Columbia \hfill 2008


# Grants

Gonçalves da Silva A. Population genomics of orange roughy in Tasmania. South East Trawl Fishing Industry Association/CSIRO – AUD 132,000.00 (2011-2012).

Gonçalves da Silva A. (co-PI with M Russello). Conservation of Amazonian tapirs. National Geographic Society Conservation Fund – USD 20,000.00 (2007-2009).

Gonçalves da Silva A. (co-PI with M Russello). Conservation of Amazonian tapirs. The Rufford Foundation Small Grants – GBP 5,000.00 (2007-2009).

Gonçalves da Silva A. Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. The Rufford Foundation Small Grants – GBP 5,000.00 (2004-2006).

Gonçalves da Silva A. Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. Disney Worldwide Emergency Conservation Fund – USD 3,500 (2005).

Gonçalves da Silva A. Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. American Society of Mammalogists –USD 1,500 (2003).

Gonçalves da Silva A. Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. The Explorer's Club Exploration Grant – USD 1,000 (2003).

<!-- # References -->

<!-- Available upon request, though likely would include Karl Pearson and Ronald A. Fisher. Please send corrections, feedback, or details of missed publications (of which there are probably a few) to svmille@clemson.edu. -->