---
title: "CV"
author: "Anders Gonçalves da Silva, PhD"
editor_options:
  chunk_output_type: console
output:
  pdf_document:
    latex_engine: pdflatex
    template: /Users/andersgs/dev/andersgs/mycv/templates/svm-latex-cv.tex
  html_document:
    df_print: paged
fontawesome: yes
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
geometry: margin=1in
github: andersgs
jobtitle: Senior Bioinformatician | Microbiological Diagnostic Lab Public Health Laboratory
keywords: R Markdown, academic CV, template
linkcolor: blue
email: anders.goncalves@unimelb.edu.au
address: Peter Doherty Institute for Immunity and Infection, The University of Melbourne
twitter: '@drandersgs'
updated: no
urlcolor: blue
---

# Employment

*BC Centre for Disease Control Public Health Laboratory, BC Centre for Disease Control*

Consultant \hfill 2020-

*Microbiological Diagnostic Unit Public Health Laboratory, The Univesity of Melbourne*

Senior Bioinformatician \hfill 2018-

*Microbiological Diagnostic Unit Public Health Laboratory, The Univesity of Melbourne*

Bioinformatician \hfill 2015-2018

*Ornithology Lab, Monash University*

Postdoctoral Researcher \hfill 2012-2015

*CSIRO Marine and Atmospheric Research*

Postdoctoral Fellow \hfill 2009-2012

*Ecological and Conservation Genomics Lab, University of British Columbia*

Postdoctoral Teaching and Research Fellow \hfill 2007-2009


# Education

*Columbia University*, PhD Ecology and Evolutionary Biology \hfill 2007

*Columbia University*, MSc Ecology and Evolutionary Biology \hfill 2004

*Columbia University*, MA Conservation Biology \hfill 2003

*Universidade Estadual de Campinas*, BSc Biology \hfill 2000


# Service and Leadership

*Leadership* of the AusTrakka Development Team.

*Leadership* of the MDU PHL Bioinformatics Team.

*Leadership* of the national CDGN Bioinformatics Working Group.

*Leadership* of the MDU/DHHS Partnership Grant.

*Leadership* in AusTrakka (data sharing for public health).

*Leadership* in development of best practices for accreditation of Bioinformatics software for use in public health.

*Leadership* in development of national proficiency testing programs for Next Generation Sequencing and Bioinformatics software.

*Leadership* in development of a national pathogen surveillance platform based on genomic data.


# Publications

## Journal Articles

```{r, echo=FALSE, message=FALSE, results='asis'}
suppressPackageStartupMessages(library(RefManageR))
library(glue)
bib <- ReadBib("bibfiles/publications.bib")
for(year in 2021:2012) {
  print(glue("### {year}"))
  print(bib[year = glue("{year}")],  .opts = list(bib.style = "authoryear"))
  print(glue(" "))
}
```

## Reports

```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/reports.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

## Book Chapters

```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/book-chapter.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

## Recent Conference Presentations
```{r, echo=FALSE, results="asis"}
bib <- ReadBib("bibfiles/conferences.bib")
print(sort(bib, sorting = 'ydnt', decreasing = T), .opts = list(bib.style = "authortitle"))
```

# Students

## PhD

*Sara Zufan* --- Department of Microbiology and Immunology, The University of Melbourne

*Courtney Lane* --- Department of Microbiology and Immunology, The University of Melbourne

*Andrew Buultjens* --- Department of Microbiology and Immunology, The University of Melbourne [Completed]

## MSc

*Andre Tan* --- Faculty of Science, The University of Melbourne [Completed]

*Gabriela Pinho* --- Instituto Nacional de Pesquisas da Amazônia [Completed]

## Honours

*Tiffany Miller-Scott* --- School of Biological Sciences, Monash University [Completed]

# Teaching

## Workshops

Genomic Epidemiology of Infectious Diseases. McGill Summer Institute in Infectious Diseases & Global Health \hfill 2018

Genomic Epidemiology of Infectious Diseases. McGill Summer Institute in Infectious Diseases & Global Health \hfill 2017 

Introductory Course in Public Health Microbial Genomics \hfill 2017

Introductory Course in Public Health Microbial Genomics \hfill 2016

Australian Pathogen Bioinformatics Symposium (ANU) \hfill 2014

Population and landscape genomics workshop (ANU) \hfill 2014

## Units

BINF90002: Elements of Bioinformatics (Lecturer) - The University of Melbourne \hfill 2017

BIOL 203: Introduction to Ecology (Instructor) – University of British Columbia \hfill 2009

GEOG 213: Introduction to Environmental Issues (Instructor) – University of British Columbia \hfill 2008


# Grants

Real-time Combined Genomic and Epidemiological Monitoring of COVID-19 in British Columbia. MSFHR - (2020-2022)

AusTrakka: real-time pathogen genomics surveillace. Commonwealth Department of Health - AUD $1,160,000 (2020-2022).

AusTrakka: real-time pathogen genomics surveillace. Victorian State Government - AUD 800,000 (2020-2022).

Tracking COVID-19 using genomics. MRFF - AUD 3,270,000 (2020-2022)

PPHAGE: Precision Public Health in Australia through Integrated Pathogen Genomics - NHMRC AUD 2,000,000 (2020-2025)

Population genomics of orange roughy in Tasmania. South East Trawl Fishing Industry Association/CSIRO – AUD 132,000.00 (2011-2012).

Conservation of Amazonian tapirs. National Geographic Society Conservation Fund – USD 20,000.00 (2007-2009).

Conservation of Amazonian tapirs. The Rufford Foundation Small Grants – GBP 5,000.00 (2007-2009).

Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. The Rufford Foundation Small Grants – GBP 5,000.00 (2004-2006).

Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. Disney Worldwide Emergency Conservation Fund – USD 3,500 (2005).

Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. American Society of Mammalogists –USD 1,500 (2003).

Landscape and conservation genetics of mammals in the Brazilian Atlantic Forest. The Explorer's Club Exploration Grant – USD 1,000 (2003).

<!-- # References -->

<!-- Available upon request, though likely would include Karl Pearson and Ronald A. Fisher. Please send corrections, feedback, or details of missed publications (of which there are probably a few) to svmille@clemson.edu. -->